% multiple1902 <multiple1902@gmail.com>
% meta.tex
% Copyright 2011~2012, multiple1902 (Weisi Dai)
% https://code.google.com/p/xjtuthesis/
% 
% It is strongly recommended that you read documentations located at
%   http://code.google.com/p/xjtuthesis/wiki/Landing?tm=6
% in advance of your compilation if you have not read them before.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Weisi Dai.
%
\ctitle{蛋清中溶菌酶的分离提取和性质实验}
\cauthor{高旭帆，郭骐瑞，程肖然，黎博琛}
\csubject{生命科学综合实验\Rnum{1}}
\csupervisor{孔宇，李华}
\ckeywords{溶菌酶；分离提取；阳离子交换色谱；SDS-PAGE}
\cproddate{\the\year 年\the\month 月}
\ctype{实验研究}

\etitle{Separation and Extraction of Lysozyme from Egg White and Characterization}
\eauthor{Xufan Gao, Qirui Guo, Xiaoran Cheng, Bochen Li}
\esupervisor{Yu Kong, Hua Li}
\ekeywords{Lysozyme; Separation and Extraction; Cation exchange chromatography; SDS-PAGE}
\ecate{Biology}
\esubject{Integrated Experiments of Life Sciences \Rnum{1}}
\eproddate{\monthname{\month}\ \the\year}
\etype{Experimental Research}

\cabstract{
溶菌酶是一种能水解N-­乙酰胞壁酸 (NAM)和N­-乙酰氨基葡萄糖之间的 β­-1,4糖苷键，从而破坏细菌细胞壁的酶，目前已广泛应用于食品、医疗、生物等产业。但是这种天然产物的分离纯化方法还有待完善。本研究从蛋清中提取溶菌酶，用阳离子交换和凝胶层析的方法进行纯化，并测定溶菌酶浓度和检测其抗菌活性。最终通过对SDS-PAGE实验结果进行比较分析，发现阳离子交换的方法可以达到更好的纯化效果，使样品中基本上不含杂蛋白。纯化得到的样品的比活力达到13\emph{.}4，回收率达到非常可观的92\emph{.}4\%。最后，通过探究不同方程对于数据的拟合，发现并解释了函数\(f(t)=at^2 + bt + c\)在拟合时更好的表现。经过提取纯化后的溶菌酶结合可控释放和酶固定化的技术将在食品储存和医疗保健领域得到应用。
%向那些疯狂的家伙们致敬, 
%他们特立独行, 
%他们桀骜不训, 
%他们惹是生非, 
%他们格格不入.
%
%他们用与众不同的眼光看待事物, 
%他们不喜欢墨守成规, 
%他们也不愿安于现状.
%
%你可以赞美他们, 引用他们, 反对他们, 
%质疑他们, 颂扬或是诋毁他们, 
%但唯独不能漠视他们. 
%
%因为他们改变了事物. 
%他们推动人类向前发展. 
%
%或许他们是别人眼里的疯子, 
%但却是我们眼中的天才. 
%
%因为只有那些疯狂到以为自己能够改变世界的人, 
%才能真正地改变世界. 
}

\eabstract{
Lysozyme is a kind of enzyme that can hydrolyze the β-1,4 glycosidic
bond between N-acetyl muramic acid (NAM) and N-acetyl glucosamine, thus
destroy the bacterial cell wall. Nowadays, they have been widely applied
to food, medical, and biological industries. However, the separation and
purification methods still need perfection for this natural product. In
this work, lysozyme was extracted from egg white and purified by cation exchange and gel chromatography. Its concentration was determined and
its antibacterial activity was tested. Finally, through the comparative
analysis of SDS-PAGE experimental results, it is found that cation exchange can achieve a better purification effect so that the
sample basically does not contain other proteins. The specific activity
of the sample purified reached \(13.4\mathrm{U\cdot mg^{ - 1}}\), and
the recovery rate reached \(92 .  4\%\). Finally, by exploring the
fitting of different equations to the data, it is found and explained
that the function \(f(t)= at ^ 2 +  bt  +  c \) performs best in the
fitting. The purified lysozyme combined with controlled release and
enzyme immobilization technology will be applied in the field of food
storage and health care.

%Here's to the crazy ones. The misfits. The rebels. The troublemakers. The round pegs in the square holes. 
%
%The ones who see things differently. They're not fond of rules. And they have no respect for the status quo. You can quote them, disagree with them, glorify or vilify them. 
%
%About the only thing you can't do is ignore them. Because they change things. They push the human race forward. 
%
%While some may see them as the crazy ones, we see genius. Because the people who are crazy enough to think they can change the world, are the ones who do.
%
%(Apple Inc.)

}
