% multiple1902 <multiple1902@gmail.com>
% meta.tex
% Copyright 2011~2012, multiple1902 (Weisi Dai)
% https://code.google.com/p/xjtuthesis/
% 
% It is strongly recommended that you read documentations located at
%   http://code.google.com/p/xjtuthesis/wiki/Landing?tm=6
% in advance of your compilation if you have not read them before.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Weisi Dai.
%
\ctitle{蛋清中溶菌酶的提取、分离条件优化和性质实验}
\cauthor{高旭帆，郭骐瑞，程肖然，黎博琛}
\csubject{生命科学综合实验\Rnum{1}}
\csupervisor{孔宇}
\ckeywords{溶菌酶；提取；分离纯化；条件优化}
\cproddate{\the\year 年\the\month 月}
\ctype{实验研究}

\etitle{Optimization of Extraction, Separation Conditions of Lysozyme from Egg White and Characterization}
\eauthor{Xufan Gao, Qirui Guo, Xiaoran Cheng, Bochen Li}
\esupervisor{Yu Kong}
\ekeywords{Lysozyme; Extraction; Separation and Purificaiton; Optimization}
\ecate{Biology}
\esubject{Integrated Experiments of Life Sciences \Rnum{1}}
\eproddate{\monthname{\month}\ \the\year}
\etype{Experimental Research}

\cabstract{
溶菌酶是一种能水解N-乙酰胞壁酸(NAM)和N-乙酰氨基葡萄糖之间的β-1,4糖苷键，从而破坏细菌细胞壁的酶，目前已广泛应用于食品、医疗、生物等产业。但是这种天然产物的分离纯化方法还有待完善。本研究从蛋清中提取溶菌酶，用阳离子交换和SDS-PAGE的方法进行纯化，用考马斯亮蓝G250测定溶菌酶浓度，并检测其抗菌活性。我们希望这些溶菌酶能够应用于食品储存和医疗保健产品。
	
（注：我们希望锻炼英文，所以希望把正文写成英文版的，但因为毕设格式和英文文章的文内参考文献格式冲突，故按照英文的。希望老师给出建议！）
%向那些疯狂的家伙们致敬, 
%他们特立独行, 
%他们桀骜不训, 
%他们惹是生非, 
%他们格格不入.
%
%他们用与众不同的眼光看待事物, 
%他们不喜欢墨守成规, 
%他们也不愿安于现状.
%
%你可以赞美他们, 引用他们, 反对他们, 
%质疑他们, 颂扬或是诋毁他们, 
%但唯独不能漠视他们. 
%
%因为他们改变了事物. 
%他们推动人类向前发展. 
%
%或许他们是别人眼里的疯子, 
%但却是我们眼中的天才. 
%
%因为只有那些疯狂到以为自己能够改变世界的人, 
%才能真正地改变世界. 
}

\eabstract{
Lysozymes are a kind of enzyme which can hydrolyze β-1,4 glycosidic bond between N-acetyl muramic acid (NAM) and N-acetyl glucosamine, thus destroy bacterial cell wall. Nowadays, they have been widely applied to food, medical, and biological industries. However, separation and purification methods still needs perfection for this natural product. In this work, we extracted lysozymes from egg white, purified them with cation exchange and SDS-PAGE, determined their concentration using Comas Brilliant Blue G250, and tested their antibacterial activity. We hope these lysozymes could be applied to food storage and health-care products.

%Here's to the crazy ones. The misfits. The rebels. The troublemakers. The round pegs in the square holes. 
%
%The ones who see things differently. They're not fond of rules. And they have no respect for the status quo. You can quote them, disagree with them, glorify or vilify them. 
%
%About the only thing you can't do is ignore them. Because they change things. They push the human race forward. 
%
%While some may see them as the crazy ones, we see genius. Because the people who are crazy enough to think they can change the world, are the ones who do.
%
%(Apple Inc.)

}
