\documentclass[a4paper,10pt]{article}

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{./Integrate Experimental.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\begin{document}
    \section{Discussion on our application}
    Given the ability to lyse the cell wall of bacterial,
    lysozyme has been attracting immense attention as a kind of 
    environment-friendly or organs-friendly antimicrobial.
    As we have discussed before,it has nowadays more and more applications
    in food-industry and clinical procedure.In this part we will discuss 
    it's applications within our preperations and capabilities.
    \subsection{Applications in food industry}
    Our fist focus is on the food industry.Since 1800s when Napoléon launch his
    strategy to conquer the europe,the storage or preservation of food has become 
    a major question in food industry.Sealing food in cans,High temperture treatment
    ,Pasteuriztion ,neumerous methods had been risen.And in the last,people introduced
    chemical additives to the food industry .Effcient as it is,nowsdays people are having 
    less tolerance in that chemical industry.Due to the conception of eating healthy,they prefer
    so-called "Non-additive food" to chemical treated food.But the lack of bacterial inhibition
    will easily make it a perfect bacterial petri dish .The chemical hazard vanishes,but the microbral
    hazard just arises.We need another method!
    
    So we cast our sight to the biological method to preserve food.In our case ,we are planning to 
    introduce lysozyme to food packing and food additives.As for the food packing ,we are going to
    distribute the lysozyme agent,in gluten\citep{Conte2006} or onto a chitosan powder, on the food packages ,mostly LDPE,this methods have been taken into 
    practice\citep{Borzooeian2017}.And its function to extend to shelf life of foods had been proved.\citep{Lian2012,Alhazmi2014} our points of
    view ,this kind of application suits our capability very well,and we have put it into our first consideration.

    Another important application in food industry is the food additive.We can add some lysozyme into specific easy-deteriorating foods，
    for example wurst,can-foods and diary.The addition of lysozyme will significant extend the preserve half life of food,these lysozymes are
    presented into chitosan particals\citep{Wu2017},this will not only protect the origin flavour of the food,but also enhance its ability to inhibit 
    bacterial emerging.
    \subsection{Clinical applications}
    The lysozyme can also plays an impressive role in clinical procedure.Like the food industry,medical is also
    a battel against bacterial.In 1676, Anton van Leeuwenhoek observed bacteria and other microorganisms, using a single-lens microscope of his own design.
    In 1796, Edward Jenner developed a method using cowpox to successfully immunize a child against smallpox. The same principles are used for developing vaccines today.
    Following on from this, in 1857 Louis Pasteur also designed vaccines against several diseases such as anthrax, fowl cholera and rabies as well as pasteurization for food preservation.
    In 1867 Joseph Lister is considered to be the father of antiseptic surgery. By sterilizing the instruments with diluted carbolic acid and using it to clean wounds, post-operative infections were reduced, making surgery safer for patients.
    In 1929 Alexander Fleming developed the most commonly used antibiotic substance both at the time and now: penicillin.\citep{Brock2003}.The emerge of antibiotic medicine start a new era for human,we can sometime beat the infection of microbes.

    But there still exists a fatal problem:ALLERGY.Some antibiotic will lead to accute allergic phenomenon,which are sometimes fatal.So we come up with this idea to 
    introduce lysozyme to health-care products. We want to introduce it in for instance dentifrices, mouth-rinses, moisturizing gels ,chewing gums or such sterllization products.\citep{Tenovuo2002}
    We try to develop a kind of lysozyme coverd badage in which the lysozyme exist in gel,or in other advanced status,such as carbon nanotubes.
    These are our prospects of the clinical application of lysozyme
    \printbibliography[title={Bibliography}] 
\end{document}